Weld pool detection and geometrical analysis during GTAW process by image processing library

### 2011-05-31 articles/TIG/paper_bain.tex

. Most of them required complex image analysis using hierarchy decomposition (structural), fractal or stochastic models (model based) and Fourier or wavelet transforms (transforms methods) 
 Di BLA BLA use this  has been thedescribe  where the shadows zones are the projection of the macro drop and droplet.

>>>>

. Most of them required complex image analysis using
 hierarchy decomposition (structural), fractal or stochastic model
s (model based) and Fourier or wavelet transforms (transforms methods) 
 Di BLA BLA use this  has been thedescribe  where the shadows zones are the projection of the macro drop and droplet.
